Mossy Pond mrmr model 1

### 2024-11-14 code/R/MossyPond_Classic_mrmr.Rmd
rename file

# Load .csv of all captures from the Mossy Pond CMR study period
captures <- read.csv("Capture_Data.csv")

@@

# ATTEMPT TO FIGURE THE PROBLEM OUT
# Include only a subset of columns from captures. This seems to have worked in the past. 
### captures <- unique(captures[ , c(2,3,5,7)])
  # when I create this subset, 5 observations disappear
  # This subset didn't work. Lets try getting rid of CA lake id column
captures <- unique(captures[ , c(3,5,7)])
  # another 2 observations disappeared
# I have not yet run this model

>>>>

# Load .csv of all captures from the Mossy Pond CMR study period
captures <- read.csv("/Users/johnimperato/Documents/Capture_Data.csv")

@@

# ATTEMPT TO FIGURE THE PROBLEM OUT
# Include only a subset of columns from captures. This seems to have worked in the past. 
### captures <- unique(captures[ , c(2,3,5,7)])
  # when I create this subset, 5 observations disappear
  # This subset didn't work. Lets try getting rid of CA lake id column
captures <- unique(captures[ , c(3,5)])
  # another 2 observations disappeared
# I have not yet run this model
